An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-04-06 simplified_sdc_intro/paper.tex
update network

Our final set of 35 nuclei are $\mathrm{n}$, ${}^{1}\mathrm{H}$,
${}^{4}\mathrm{He}$, ${}^{12}\mathrm{C}$, ${}^{14}\mathrm{C}$,
${}^{13}\mathrm{N}$, ${}^{14}\mathrm{N}$, ${}^{16}\mathrm{O}$,
${}^{18}\mathrm{O}$, ${}^{18}\mathrm{F}$, ${}^{20}\mathrm{Ne}$,
${}^{21}\mathrm{Ne}$, ${}^{22}\mathrm{Ne}$, ${}^{22}\mathrm{Na}$,
${}^{23}\mathrm{Na}$, ${}^{23}\mathrm{Mg}$, ${}^{24}\mathrm{Mg}$,
${}^{27}\mathrm{Al}$, ${}^{27}\mathrm{Si}$, ${}^{28}\mathrm{Si}$,
${}^{31}\mathrm{P}$, ${}^{31}\mathrm{S}$, ${}^{32}\mathrm{S}$,
${}^{35}\mathrm{Cl}$, ${}^{36}\mathrm{Ar}$, ${}^{39}\mathrm{K}$,
${}^{40}\mathrm{Ca}$, ${}^{43}\mathrm{Sc}$, ${}^{44}\mathrm{Ti}$,
${}^{47}\mathrm{V}$, ${}^{48}\mathrm{Cr}$, ${}^{51}\mathrm{Mn}$,
${}^{52}\mathrm{Fe}$, ${}^{55}\mathrm{Co}$, ${}^{56}\mathrm{Ni}$.  The 119
rates linking them are given in table~\ref{table:rates}, with the
forward rates having a positive $Q$ value and the reverse having a
negative $Q$ value.  We add screening to the rates using the prescription
from \citet{graboske:1973,alastuey:1978,itoh:1979}.  The C++ code for the network is output by \pynucastro\
directly for \castro.  A graphical overview of the network showing the links
between the nuclei is shown in figure~\ref{fig:subch_network}.

@@

${}^{14}\mathrm{C} + {}^{4}\mathrm{He} \rightarrow {}^{18}\mathrm{O}$ & 
  ${}^{18}\mathrm{O} \rightarrow {}^{4}\mathrm{He} + {}^{14}\mathrm{C}$ \\
${}^{14}\mathrm{C} \rightarrow {}^{14}\mathrm{N}$ & 

@@

@@

${}^{16}\mathrm{O} + {}^{16}\mathrm{O} \rightarrow \mathrm{n} + {}^{31}\mathrm{S}$ & 

@@

${}^{18}\mathrm{O} + {}^{4}\mathrm{He} \rightarrow {}^{22}\mathrm{Ne}$ & 
  ${}^{22}\mathrm{Ne} \rightarrow {}^{4}\mathrm{He} + {}^{18}\mathrm{O}$ \\

@@

${}^{18}\mathrm{F} \rightarrow {}^{18}\mathrm{O}$ & 

@@

${}^{22}\mathrm{Ne} + {}^{1}\mathrm{H} \rightarrow {}^{23}\mathrm{Na}$ & 
  ${}^{23}\mathrm{Na} \rightarrow {}^{1}\mathrm{H} + {}^{22}\mathrm{Ne}$ \\
${}^{22}\mathrm{Na} \rightarrow {}^{22}\mathrm{Ne}$ & 

@@

${}^{23}\mathrm{Mg} + \mathrm{n} \rightarrow {}^{24}\mathrm{Mg}$ & 

@@

${}^{27}\mathrm{Si} + \mathrm{n} \rightarrow {}^{28}\mathrm{Si}$ & 

@@

${}^{31}\mathrm{S} + \mathrm{n} \rightarrow {}^{32}\mathrm{S}$ & 

@@

 &  ${}^{12}\mathrm{C} + {}^{12}\mathrm{C} \rightarrow \mathrm{n} + {}^{23}\mathrm{Mg}$ \\
 &  ${}^{16}\mathrm{O} + {}^{12}\mathrm{C} \rightarrow \mathrm{n} + {}^{27}\mathrm{Si}$ \\

>>>>

Our final set of 28 nuclei are ${}^{1}\mathrm{H}$, ${}^{4}\mathrm{He}$, ${}^{12}\mathrm{C}$, ${}^{13}\mathrm{N}$, ${}^{14}\mathrm{N}$, ${}^{16}\mathrm{O}$, ${}^{18}\mathrm{F}$, ${}^{20}\mathrm{Ne}$, ${}^{21}\mathrm{Ne}$, ${}^{22}\mathrm{Na}$, ${}^{23}\mathrm{Na}$, ${}^{24}\mathrm{Mg}$, ${}^{27}\mathrm{Al}$, ${}^{28}\mathrm{Si}$, ${}^{31}\mathrm{P}$, ${}^{32}\mathrm{S}$, ${}^{35}\mathrm{Cl}$, ${}^{36}\mathrm{Ar}$, ${}^{39}\mathrm{K}$, ${}^{40}\mathrm{Ca}$, ${}^{43}\mathrm{Sc}$, ${}^{44}\mathrm{Ti}$, ${}^{47}\mathrm{V}$, ${}^{48}\mathrm{Cr}$, ${}^{51}\mathrm{Mn}$, ${}^{52}\mathrm{Fe}$, ${}^{55}\mathrm{Co}$, ${}^{56}\mathrm{Ni}$.  The 107
rates linking them are given in table~\ref{table:rates}, with the
forward rates having a positive $Q$ value and the reverse having a
negative $Q$ value.  We add screening to the rates using the prescription
from \citet{graboske:1973,alastuey:1978,itoh:1979}.  The C++ code for the network is output by \pynucastro\
directly for \castro.  A graphical overview of the network showing the links
between the nuclei is shown in figure~\ref{fig:subch_network}.

@@

${}^{12}\mathrm{C} + {}^{12}\mathrm{C} \rightarrow {}^{24}\mathrm{Mg}$ & 

@@

${}^{16}\mathrm{O} + {}^{12}\mathrm{C} \rightarrow {}^{28}\mathrm{Si}$ & 

@@

${}^{16}\mathrm{O} + {}^{16}\mathrm{O} \rightarrow {}^{32}\mathrm{S}$ & 

@@

@@

@@

@@

@@

@@

@@
